|

### 2016-06-24 Manuals/PrideID/Manual-PrideID.Rmd
pride fix slow download

### Pride ID

@@

```
cd ~/Desktop/PXD001468
ls
```
If other PrideID is desired, change the PRIDEID option on the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).

>>>>

@@

```
cd ~/Desktop/PXD001468
```
in this case, ```p3.config``` must have the following fields:
```
REPO = PRIDE
PRIDEID = (e.g: PXD001468) 
RUN_MSGF = (e.g: YES)
METHOD = (e.g: SPECTRUM_COUNT)
```

If other PrideID is desired, change the PRIDEID option in the p3.config. Ensure that the corresponding PrideID have the required files (\*.fasta, \*.mzml, etc.).
